Our Title

### 2015-05-05 draft.tex
Added in revisions to Section 5.5 "Detection Technologies", and moved much of it into the new Appendix D. Added in links to Appendix D where they had placeholders before.

The age of the physics package is determined from the composition. Because SNM is, itself, radioactive, a small amount of mass is converted to heat and radiates off. It is possible to approximate the change in mass by estimating the age of the original physics package based on the apparent design of the weapon; this change in mass correlates to the age of the device since the physics package was created \cite{Inn2013}. See

\subsection{?????? This section hasn't been created yet  ???????}

\enquote{Methods of Active Interrogation,}

\subsection{??????  Add ref to this Tech Appendix, once it's done   ??????}

in \autoref{} for a description of the technical means of estimating the composition of SNM. The country of origin for Uranium-based weapons may be narrowed down based on the initial enrichment of the material \cite{Defense1998}. The facility of origin may be determined in Plutonium-based designs based on the ratio of isotopes present, as shown in \autoref{fig:pu_signatures}.

@@

\section{Detection technologies }

\subsection{????? Recommend developing short (~1 page or less) overview of some of the high level considerations involved in detecting nuclear material, limitations, and current programs.  Place the remainder of the material, basically what is included here, into an Appendix.  Did not grammar review.   ?????}

\subsection{Fission Weapons}

   \subsubsection{Passive Signals}

\subsubsection{Active Signals}

% \myparagraph{Introduction to Active Interrogation}
\textbf{Introduction to Active Interrogation}

\textbf{Nuclear Resonance Fluorescence}

\textbf{Neutron Interrogation}

The primary advantage of this technique is is that the systems are very small (\textless\ 0.2 m\(^3\)), light weight (\textless\ 12 kg), and use very little power (\textless\ 50 W) \cite{Chichester2009}.  Another major benefit is that research indicates this method will not subject the cargo to an excessive dose of radiation \cite{Hall2007}.  One major downside of this method is that it seems like research is still being conducted to determine if this method will work for a full size ago container \cite{Hall2007}.  A second major downside is that current technology requires the sample to be less than a meter from the detector, approximately 91.4 cm \cite{Hall2007}. A major technical downside of this technology is that, because it works by inducing fissions, it is only able to detect fissionable material.

\subsection{Strategies for detecting RDD}

\subsubsection{Passive Signals}

\subsubsection{Shielding of Radioactive Materials}  \label{sec:shielding_mat}

\subsubsection{????????  This section needs MASSIVE cleaning up ????????}

Of the radiation types mentioned: alpha, beta, and gamma, the gamma emitters are by far the farthest penetrating, most energetic, radioisotope emitters listed.  The shielding suggested will merely attenuate the energy levels of the gamma emissions, but in essence the emission passes through the shielding and continues on its travel through the medium. \autoref{fig:shielding_reqs} shows relative stopping distances in materials for given radiation types. Alphas, although they can be very energetic upon initial release from the source, are very large particles in comparison to the surroundings.  It is more likely that the 2+ charged alpha ion will interact with matter than the other radiation types, even as depicted a piece of paper is sufficient shielding material to attenuate alpha emissions.

@@

@@

\subsubsection{?????????  Add in cross-reference to below paragraph, once Tech Appendix is made  ??????????? }

This document suggests the aggressive continued advancement of such programs. The continued development of new technologies, as outlined in \autoref{}, must be exploited for every feasible advancement leading to total success in national security. This document suggests a priority-phased plan outlining a strong technological collaboration with government labs, similar to the plan put forth in 2005, in order to develop and deploy the next generation of RPMs \cite{Simmons2005}. Such a plan would be managed by the DNDO and executed by the CPB and AAPA. This plan, however, can only be effective given the successfully executed deployment of any developing technology. Technological failures such as the ASP development program are acceptable so long as workable alternatives exist.

@@

>>>>

The age of the physics package is determined from the composition. Because SNM is, itself, radioactive, a small amount of mass is converted to heat and radiates off. It is possible to approximate the change in mass by estimating the age of the original physics package based on the apparent design of the weapon; this change in mass correlates to the age of the device since the physics package was created \cite{Inn2013}. See \autoref{sec:intro_active_interrogation}, \enquote{Introduction to Active Interrogation,} in \autoref{app:tech} for a description of the technical means of estimating the composition of SNM. The country of origin for Uranium-based weapons may be narrowed down based on the initial enrichment of the material \cite{Defense1998}. The facility of origin may be determined in Plutonium-based designs based on the ratio of isotopes present, as shown in \autoref{fig:pu_signatures}.

@@

\section{Detection Technologies}

The National Nuclear Security Administration (NNSA) collaborates the efforts of the Defense Threat Reduction Agency (DTRA), the U.S. National Laboratories, and other federal agencies to locate and identify special nuclear material \cite{NationalNuclearSecurityAdministration}. Detection of radioisotopes requires an understanding of the type and energy of radiation and the material response in detection systems (see \autoref{app:tech} for a discussion of passive and active detection of the radioactive materials employed in fission weapon and a radiation dispersal device). As a general overview, the success of the detection of radioactive materials relies on specialized equipment, minimizing the distance to the material, collection time to improve statistics and resolve a signal above background, and, in some circumstances, utilizing reach back for specialized interpretation of the results.

Presumably, the clandestine transport of SNM will be shielded to reduce or eliminate the apparent signal available to detection systems outside the transport container. The cost of search and seizure of every container across international borders is prohibitively expensive. The alternative searching method favored by the NNSA is standoff, active interrogation, where an interrogating beam of neutrons or gamma rays is used to induce a high energy signal from radioactive materials hidden behind shielding. The application of active interrogation is only effective if a significant portion of traffic into each country is subject to search (see \autoref{app:tech}  for a discussion of the benefits and disadvantages of active interrogation). However, it is worth noting that active portal monitoring is expensive and would require years for systematic deployment, but passive monitoring stations could be employed more rapidly \cite{Grogan201362}.

\subsection{Shielding of Radioactive Materials}  \label{sec:shielding_mat}

Of the radiation types mentioned (alpha, beta, and gamma), the gamma emitters are by far the farthest penetrating, most energetic, radioisotope emitters listed \cite{krane1987introductory}.  The shielding suggested will merely attenuate the energy levels of the gamma emissions, but in essence the emission passes through the shielding and continues on its travel through the medium. \autoref{fig:shielding_reqs} shows relative stopping distances in materials for given radiation types.

@@

Alphas, although very energetic upon initial release from the source, are very large particles in comparison to the surroundings.  It is more likely that the 2+ charged alpha ion will interact with matter than the other radiation types; even as depicted, a piece of paper is sufficient shielding material to attenuate alpha emissions \cite{krane1987introductory}. Thus, shielding SNM to prevent detection of its alpha signatures is unnecessary, as the air in between the SNM and a detector (more than a few cm away) would shield the alpha particles \cite{Cember2008}.

To shield SNM against the more penetrating beta particles and neutrons, water, concrete, paraffin, high-density plastics, or boron-based materials (such as boron carbide or borosilicate glass) could be easily used \cite{Cember2008}. These would not only shield against passive detection of the SNM, but against neutron interrogation - based active detection methods as well, given a few feet of shielding \cite{Grogan201362}.

To shield SNM against gamma rays and X-rays, lead and concrete would be the most common choices of material \cite{Cember2008}.  These would not only shield against passive detection of the SNM, but against X-ray fluorescence - based active detection methods as well, given more than several inches of lead shielding \cite{PhysRevC.78.041601,Grogan201362,Bertozzi2005}.

Thus, the most  effective shielding to prevent passive or active detection of SNM would likely be a combination of layers of paraffin (preferably boron-impregnated) and lead.

@@

This document suggests the aggressive continued advancement of such programs. The continued development of new technologies, as outlined in \autoref{app:tech}, must be exploited for every feasible advancement leading to total success in national security. This document suggests a priority-phased plan outlining a strong technological collaboration with government labs, similar to the plan put forth in 2005, in order to develop and deploy the next generation of RPMs \cite{Simmons2005}. Such a plan would be managed by the DNDO and executed by the CPB and AAPA. This plan, however, can only be effective given the successfully executed deployment of any developing technology. Technological failures such as the ASP development program are acceptable so long as workable alternatives exist.

@@

\chapter[Appendix D: Technology]{Technology} \label{app:tech}

\section{Fission Weapons}

   \subsection{Passive Signals}

\subsection{Active Signals}

% \myparagraph{Introduction to Active Interrogation}
\subsubsection{Introduction to Active Interrogation} \label{sec:intro_active_interrogation}

\subsubsection{Nuclear Resonance Fluorescence}

\subsubsection{Neutron Interrogation}

The primary advantage of this technique is is that the systems are very small (\textless\ 0.2 m\(^3\)), light weight (\textless\ 12 kg), and use very little power (\textless\ 50 W) \cite{Chichester2009}.  Another major benefit is that research indicates this method will not subject the cargo to an excessive dose of radiation \cite{Hall2007}.  Research is still being conducted to determine if this method will work for a full size ago container \cite{Hall2007}.  A second major downside is that current technology requires the sample to be less than a meter from the detector, approximately 91.4 cm \cite{Hall2007}. Because this method works by inducing fissions, it is only able to detect fissionable material.

\section{Strategies for detecting RDD}
